Comparing Apples and Oranges in Youth Depression Treatments?

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
Added t2 and i2 to metaregression table

# Calculate the mean and standard deviation of I2 values for each level
i2_summary_all <- data.frame(
  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
)

```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
# # B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
# #  grab ids for those studies
# cbt_fluox_esc_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
# 
# # Use those ids to subset all dataframes in the list
# # By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
# # So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
# # This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
# # We may have multiple controls per study id for this reason, though this isn't a problem 
# # conceptually.
# 
# list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
#   df %>%
#     filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
#     filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
# })
# 
# # count the number of studies
# cbt_fluox_esc_study <- df_long_for_metan %>%
#   filter(new_study_id %in% cbt_fluox_esc_study_ids,
#          !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
# study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
# # CB checked, looks good now.
# 
# # apply the metareg function to the list of cbt, fluox, esc
# model_1 <- as.formula(~ four_level_var)
# list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
# 
# # extract coefficients and model characteristics.
# condition <- levels(list_df_simulated[[1]]$four_level_var)
# aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
# aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
# 
# # extract SMDs from the list for cbt fluox escit
# means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
# 
# # calculate mean SMDs and ses
# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
# coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
#  coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
# 
# # add the ns to the dataframe
# coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>% 
#                                         ungroup() %>% 
#                                       select(condition, n),  
#                                     by = "condition")
```

@@

```{r proportion-wl, echo=FALSE}
# Filter the dataframe
filtered_df <- df_long_for_metan %>%
  filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")

# Count the occurrences of each type
type_counts <- filtered_df %>%
  count(type) %>%
  mutate(total_count = sum(n),
         wl_sum = sum(n[type == "wl"]),
         wl_percentage = wl_sum / total_count * 100)

# how many examples of matching of active and control in number of hours

instances_count <- df_descr_psy_conditions_no_wl %>%
  filter(!is.na(total_hours)) %>%
  group_by(new_study_id, total_hours) %>%
  summarise(count = n()) %>%
  filter(count > 1) %>%
  summarise(total_instances = n())

@@

@@

aggregate_results_overall <- aggregate_results_overall %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition))) %>% 
  relocate("condition", .before = "coefficients")

new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "QE", "k")

@@

flextable(table_aggregate_results_overall) %>%
  set_table_properties(width = 1) %>%
  autofit() %>%
  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
  # add_header_row(values = "Table 4", colwidths = 6) %>% 
  bold(part = "header") %>%   # Bold the relevant header rows
  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  # italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(part = "header", border = big_border) %>% 
  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")
```

@@

```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
# # G. Post SD Sensitivity Analysis ---------------------------------------
# ##--------- Data preparation
# #For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
# #create subset of first_row
# df_first_row <- read.csv(here("df_first_row.csv"))
# #create new_study_ids to match master dataset
# df_first_row  <- df_first_row  %>%
#   mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
#                                   .default = study ))
# df_first_row_reduced <- df_first_row %>%
#   filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
#   select(new_study_id, post_sd_active, post_sd_control)
# #as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
# df_first_row_reduced <- df_first_row_reduced %>%
#   group_by(new_study_id) %>%
#   slice_head(n = 1) %>%
#   ungroup()
# #create a column in master df that shows 1 if any missing post sds in first_row
# df_long_for_metan_with_missing <- df_long_for_metan %>%
#   left_join(df_first_row_reduced, by = "new_study_id") %>%
#   mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
#   select(-post_sd_active, -post_sd_control) %>%
#   arrange(arm_effect_size, new_study_id)
# #all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
# df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
#   filter(missing_post_sd == 0)
# n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
# n_distinct(df_long_for_metan$new_study_id) #88 studies total
# nrow(df_long_for_metan_without_missing) #140 arms
# nrow(df_long_for_metan) #203 arms
# ##------------ Estimates 
# #take study ids where study does not have missing post SD
# sd_study_ids <-
#   df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
# # use those ids to subset all dataframes in the list
# list_sd_study <- list()
# for(i in 1: length(list_df_simulated)){
#   list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
#                                                  %in% sd_study_ids,]
# # count the number of studies
# study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
# # apply the metareg function to the list of clinical studies
# model_1 <- as.formula(~ four_level_var)
# list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
# condition <- levels(list_df_simulated[[1]]$four_level_var)
# aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
# # extract SMDs from the list for clinical studies
# means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
# coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
# coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
# # add the ns to the dataframe
# coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>% 
#                                             ungroup() %>% 
#                                             select(condition, n),  
#                                           by = "condition")
# #H. Studies with variances <.02-----------------------------
# ##-----------Data preparation
# #create column with variance in master df
# df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
# #take study ids where variance =2 or less
# var2_study_ids <-
#   df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
# length(var2_study_ids)
# ##------------Estimates
# # use those ids to subset all dataframes in the list
# list_var2_study <- list()
# for(i in 1: length(list_df_simulated)){
#   list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
#                                                %in% var2_study_ids,]
# # count the number of studies
# study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
# # apply the metareg function to the list of clinical studies
# model_1 <- as.formula(~ four_level_var)
# list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
# condition <- levels(list_df_simulated[[1]]$four_level_var)
# aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
# # extract SMDs from the list for clinical studies
# means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
# coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
# coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
# # add the ns to the dataframe
# coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>% 
#                                           ungroup() %>% 
#                                           select(condition, n),  
#                                         by = "condition")

>>>>

# Calculate the mean and standard deviation of I2 values for each level
i2_summary_all <- data.frame(
  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
)
```

```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
#  grab ids for those studies
cbt_fluox_esc_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

# Use those ids to subset all dataframes in the list
# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox.
# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria.
# This leaves all the control conditions from trials where the active is cbt, fluox or esc.
# We may have multiple controls per study id for this reason, though this isn't a problem
# conceptually.

list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
  df %>%
    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
})

# count the number of studies
cbt_fluox_esc_study <- df_long_for_metan %>%
  filter(new_study_id %in% cbt_fluox_esc_study_ids,
         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
# CB checked, looks good now.

# apply the metareg function to the list of cbt, fluox, esc
model_1 <- as.formula(~ four_level_var)
list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)

# extract SMDs from the list for cbt fluox escit
means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)

# calculate mean SMDs and ses
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
 coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))

# add the ns to the dataframe
coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>%
                                        ungroup() %>%
                                      select(condition, n),
                                    by = "condition")
```

@@

```{r proportion-wl, echo=FALSE}
# Filter the dataframe
# filtered_df <- df_long_for_metan %>%
#   filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
# 
# # Count the occurrences of each type
# type_counts <- filtered_df %>%
#   count(type) %>%
#   mutate(total_count = sum(n),
#          wl_sum = sum(n[type == "wl"]),
#          wl_percentage = wl_sum / total_count * 100)
# 
# # how many examples of matching of active and control in number of hours
# 
# instances_count <- df_descr_psy_conditions_no_wl %>%
#   filter(!is.na(total_hours)) %>%
#   group_by(new_study_id, total_hours) %>%
#   summarise(count = n()) %>%
#   filter(count > 1) %>%
#   summarise(total_instances = n())

@@

#add i2 to aggregate results
aggregate_results_overall_i2 <- cbind(aggregate_results_overall, 
                                   i2_2 = rep(i2_summary_all$mean_i2_level2, nrow(aggregate_results_overall)),
                                   i2_3 = rep(i2_summary_all$mean_i2_level3, nrow(aggregate_results_overall)))

@@

aggregate_results_overall_i2 <- aggregate_results_overall_i2 %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition))) %>% 
  relocate("condition", .before = "coefficients")

new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2_1", "T2_2", "QE", "k", "I2_2", "I2_3")

@@

flextable(table_aggregate_results_overall) %>%
  set_table_properties(width = 1) %>%
  autofit() %>%
  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "T2_2"],
                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "I2_3"], 
                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "I2_2"], 
                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"], "."), colwidths = 6) %>%
  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
  # add_header_row(values = "Table 4", colwidths = 6) %>% 
  bold(part = "header") %>%   # Bold the relevant header rows
  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
  # italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders around the caption that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
  hline(part = "header", border = big_border) %>% 
  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
  align(j = 1, align = "left", part = "all") %>% 
  font(fontname = "Calibri", part = "all") %>% 
  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
  line_spacing(space = .7, part = "all")
```

@@

```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
# G. Post SD Sensitivity Analysis ---------------------------------------

# apply the metareg function to the list of clinical studies
model_1 <- as.formula(~ four_level_var)
list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)

# extract SMDs from the list for clinical studies
means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
